Output Summary

### 2021-12-11 03-post-process/output-plots.Rmd

  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

  # extract posterior summaries of total parr recruits by brood year
  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))

@@

  # draw fitted relationship: Bayesian
  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)

  # draw fitted relationship: OLS
  polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
  lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
  lines(ols_R_pred[2,] ~ f_pred, lty = 2)
  lines(ols_R_pred[3,] ~ f_pred, lty = 2)
  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)

@@

```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

@@

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

  # conversion rates
  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[.+,pop]", pop = j))

@@

```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # conversion rates
  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[.+,pop]", pop = j))

@@

# create a sequence of WUL values to predict capacity at
wul_seq = seq(0, max(jags_data$wul) * 1.05, length = 30)

@@

```{r}
# extract posterior summary of slope
est = post_summ(post, "mu_beta_per_wul")
colnames(est) = "slope"

@@

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j) {
  # extract parr, scale it to WUL, and create new post object
  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
  Pa_scaled = Pa/jags_data$wul[j]
  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))

@@

  # extract/format posterior summaries of realized survivals
  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["mean",])
  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["2.5%",])
  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["97.5%",])

@@

```{r adults-per-smolt, fig.width = 6, fig.height = 5}
sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]

plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_nor, pop = j)) * 100
  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_hor, pop = j)) * 100

@@

  # plot natural origin time series
  plot_tseries(est = Ra_per_Ma_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, 10))

  # add hatchery origin time series
  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(Ra_per_Ma_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)

@@

```{r bon-to-bon, fig.width = 6, fig.height = 5}
sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]

plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))

  # get a max value for ylim
  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])

@@

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)

@@

```{r parr-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
}

@@

```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
}

@@

```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[.+,pop]", pop = j)), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)], main = pops[j])
 abline(h = 1, lty = 2)
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
```

@@

```{r n-stray, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
}

@@

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

@@

```{r maturity-plot-fn}
maturity_plot = function(j) {
  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))

>>>>

  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total parr recruits by brood year
  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))

@@

  # draw fitted relationship: Bayesian
  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)

@@

```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))

@@

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[year,pop]", pop = j, year = ts_yrs))

@@

```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

# create a sequence of WUL values to predict capacity at
wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)

@@

```{r beta-v-habitat-slope}
# extract posterior summary of slope
est = post_summ(post, "mu_beta_per_wul")
colnames(est) = "slope"

@@

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j) {
  # extract parr, scale it to WUL, and create new post object
  Pa = post_subset(post, sub_index("^Pa[year,.,pop]", pop = j, year = ts_yrs), matrix = TRUE)
  Pa_scaled = Pa/jags_data$wul[j]
  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))

@@

  # extract/format posterior summaries of realized survivals
  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["mean",])
  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["2.5%",])
  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["97.5%",])

@@

```{r adults-per-smolt, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100

@@

  # plot natural origin time series
  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

@@

```{r bon-to-bon, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))

  # get a max value for ylim
  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])

@@

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

@@

```{r parr-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

@@

```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
```

@@

```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
 abline(h = 1, lty = 2)
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
```

@@

```{r n-stray, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

@@

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

@@

```{r maturity-plot-fn}
maturity_plot = function(j) {
  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
